Implementation of Parallel Algorithms for ARIMA in Distributed Database Systems

### 2013-10-04 draft.tex
Minor changes

\begin{algorithm}[ht]
\KwIn{An initial guess for parameters $\vec{\phi}_0, \vec{\theta}_0, \mu_0$}
\KwOut{The parameters that maximize the likelihood $\vec{\phi}^*,
  \vec{\theta}^*, \mu^*$}
    $k \leftarrow 0$; $v \leftarrow 2$;
    $(\vec{\phi},\vec{\theta},\mu) \leftarrow
    (\vec{\phi}_0,\vec{\theta}_0,\mu_0)$\;
    Calculate $Z(\vec{\phi},\vec{\theta},\mu)$ with
    Eq. (9).  \textit{\footnotesize \# Vector of errors}\;
    $A \leftarrow J^T J$   \textit{\footnotesize \# The Gauss-Newton Hessian
    approximation}\;
    $u \leftarrow \tau * \max_i(A_{ii})$ \textit{\footnotesize \# Weight of the
    gradient-descent step}\;
    $g \leftarrow J^T Z(\vec{\phi},\vec{\theta},\mu)$ \textit{\footnotesize \#
    The gradient descent step}\;
	$ \text{stop} \leftarrow (\|g\|_{\infty} \le \epsilon_1)$
    \textit{\footnotesize \# Termination Variable}\;
	\While{not stop and $k < k_{\max}$}{
		$k \leftarrow k + 1$\;
		\Repeat{stop or $\rho > 0$}{
            $\delta \leftarrow{(A + u \times \text{diag}(A))}^{-1} g$
            \textit{\footnotesize \# Calculate step direction}\;
            \eIf(\textit{\footnotesize \# Change  is too small
              to
              continue.})
            {$\| \delta \| \le \epsilon_2 \|
              (\vec{\phi},\vec{\theta},\mu) \|$} {
				$\text{stop} \leftarrow \text{true}$\;
			}{
				$(\vec{\phi}_{new},\vec{\theta}_{new},\mu_{new})
                \leftarrow (\vec{\phi},\vec{\theta},\mu) + \delta$
                \textit{\footnotesize \# A trial step}\;
				$\rho \leftarrow (\|
                Z(\vec{\phi},\vec{\theta},\mu)\|^2 - \|
                Z(\vec{\phi}_{new},\vec{\theta}_{new},\mu_{new})\|^2
                )/(\delta^T(u \delta + g))$ \;
                \eIf(\textit{\footnotesize \# Trial step was good}){$\rho >
                    0$}{
					$(\vec{\phi},\vec{\theta},\mu) \leftarrow
                    (\vec{\phi}_{new},\vec{\theta}_{new},\mu_{new})$
                    \textit{\footnotesize \# Update variables}\;
                    Calculate $Z(\vec{\phi},\vec{\theta},\mu)$ with
                    Eq. (9); $A \leftarrow J^T J$; $g \leftarrow J^T
                    Z(\vec{\phi},\vec{\theta},\mu)$\;
					$ \text{stop} \leftarrow (\|g\|_{\infty} \le
                    \epsilon_1)$ or $(\|
                    Z{(\vec{\phi},\vec{\theta},\mu)}^2 \| \le
                    \epsilon_3)$ \;
                    $v \leftarrow 2$;
					$u \rightarrow u * \max(1/3, 1 - {(2\rho - 1)}^3 )$\;
                } (\textit{\footnotesize \# Trial step was bad}){
                    $v \leftarrow 2 v$;
					$u \leftarrow u v$\;
				}
			}
		 }
	}
	$(\vec{\phi}^*,\vec{\theta}^*,\mu^*) \leftarrow (\vec{\phi},\vec{\theta},\mu)$\;

>>>>

\begin{algorithm}[ht]
  \KwIn{An initial guess for parameters $\vec{\phi}_0, \vec{\theta}_0,
    \mu_0$} \KwOut{The parameters that maximize the likelihood
    $\vec{\phi}^*, \vec{\theta}^*, \mu^*$} $k \leftarrow 0$; $v
  \leftarrow 2$; $(\vec{\phi},\vec{\theta},\mu) \leftarrow
  (\vec{\phi}_0,\vec{\theta}_0,\mu_0)$\; Calculate
  $Z(\vec{\phi},\vec{\theta},\mu)$ with Eq. (9).
  \textit{\footnotesize // Vector of errors}\; $A \leftarrow J^T J$
  \textit{\footnotesize // The Gauss-Newton Hessian approximation}\;
  $u\leftarrow \tau * \max_i(A_{ii})$ \textit{\footnotesize // Weight
    of the gradient-descent step}\; $g \leftarrow J^T
  Z(\vec{\phi},\vec{\theta},\mu)$ \textit{\footnotesize // The
    gradient descent step}\; $ \text{stop} \leftarrow (\|g\|_{\infty}
  \le \epsilon_1)$ \textit{\footnotesize // Termination Variable}\;
  \While{not stop and $k < k_{\max}$}{ $k \leftarrow k + 1$\;
    \Repeat{stop or $\rho > 0$}{ $\delta \leftarrow{(A + u \times
        \text{diag}(A))}^{-1} g$ \textit{\footnotesize // Calculate
        step direction}\; \eIf(\textit{\footnotesize // Change is too
        small to continue.})  {$\| \delta \| \le \epsilon_2 \|
        (\vec{\phi},\vec{\theta},\mu) \|$} { $\text{stop} \leftarrow
        \text{true}$\; }{
        $(\vec{\phi}_{new},\vec{\theta}_{new},\mu_{new}) \leftarrow
        (\vec{\phi},\vec{\theta},\mu) + \delta$ \textit{\footnotesize
          // A trial step}\; $\rho \leftarrow (\|
        Z(\vec{\phi},\vec{\theta},\mu)\|^2 - \|
        Z(\vec{\phi}_{new},\vec{\theta}_{new},\mu_{new})\|^2
        )/(\delta^T(u \delta + g))$ \; \eIf(\textit{\footnotesize //
          Trial step was good}){$\rho > 0$}{
          $(\vec{\phi},\vec{\theta},\mu) \leftarrow
          (\vec{\phi}_{new},\vec{\theta}_{new},\mu_{new})$
          \textit{\footnotesize // Update variables}\; Calculate
          $Z(\vec{\phi},\vec{\theta},\mu)$ with Eq. (9); $A \leftarrow
          J^T J$; $g \leftarrow J^T Z(\vec{\phi},\vec{\theta},\mu)$\;
          $ \text{stop} \leftarrow (\|g\|_{\infty} \le \epsilon_1)$ or
          $(\| Z{(\vec{\phi},\vec{\theta},\mu)}^2 \| \le \epsilon_3)$
          \; $v \leftarrow 2$; $u \rightarrow u * \max(1/3, 1 -
          {(2\rho - 1)}^3 )$\; } (\textit{\footnotesize // Trial step
          was bad}){ $v \leftarrow 2 v$; $u \leftarrow u v$\; } } } }
  $(\vec{\phi}^*,\vec{\theta}^*,\mu^*) \leftarrow
  (\vec{\phi},\vec{\theta},\mu)$\;
